% Chapter Template

\chapter{Conclusion} % Main chapter title

%\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}
%\section{}
In this thesis, first some variants of hierarchical Gaussian descriptor has been tested. Three kinds variants are proposed by changing the basic pixel feature vector, changing the way to construct small patches by using superpixel segmentation and replacing the single Gaussian model with Gaussian mixture model. However, those three variants have worse performance than the original version of hierarchical Gaussian descriptor. Therefore, the original version is used in this thesis. The original version of hierarchical Gaussian descriptor characterizes the pixel by the pixel's vertical coordinate, texture and color. Then a hierarchical structure is created by modelling from pixels to patches and from patches to regions. The final dimension of this descriptor is $1* 27622$.

Furthermore, KLFDA was used to reduce the dimension of the hierarchical Gaussian descriptors, and gradient descent method was used to learn a Mahalanobis distance metric on the lower-dimensional space. By comparison, we found that the proposed metric has better performance than NFST and XQDA on the VIPeR and CUHK1 datasets, but XQDA and NFST outperformed the proposed metric learning on the Prid\_2011 and Prid\_450s. We also found that the proposed metric learning had better rank 1 score than NFST, and its performance was only second to XQDA on the GRID dataset. 


\section{Contributions}
There are three contributions in this thesis. (1) The metric learning on the dimension-reduced hierarchical Gaussian descriptor by KLFDA is studied. KLFDA is used to reduce dimension in this thesis, and the gradient descent method optimizes a Mahalanobis distance metric on the lower-dimensional space. In this thesis it has been demonstrated that extra improvement can be achieved by metric learning in this lower-dimensional space. (2) By experiment it is concluded that imperfect foreground segmentation improves performance of histogram-based descriptors but decreases performance of texture-based descriptors, which is caused by the imperfect segmentation on single-image-based foreground segmentation. (3) Some variants of the hierarchical Gaussian descriptor have been tested. LBP and superpixel segmentation were combined with the hierarchical Gaussian descriptor, but those variants had worse performance than the original hierarchical Gaussian descriptor.

\section{Future work}
\subsection{Improve the hierarchical Gaussian descriptor}
It has been demonstrated that in the basic pixel feature $\bm{f}_i$, the color components are more important than the $y$ coordinate and gradient components. LBP has been proven to be a worse choice for texture representation in $\bm{f}_i$. Therefore, one strategy to improve the hierarchical Gaussian descriptor is to find a better texture representation to replace gradient components in basic pixel feature. 
\subsection{Improve foreground segmentation algorithm}
The imperfect foreground segmentation decreases the performance of textural features. One solution is to improve the method of modelling the foreground of a single image. Another solution is to segment the foreground based on a sequence of images or a video. Video-based foreground segmentation can get better results. If the foreground can be well modelled by a video or a sequence of images so that less textural noise is created, the segmentation might improve the hierarchical Gaussian descriptor's performance.
\subsection{Decrease the computational cost of gradient descent method}
It is important to reduce the computational cost of the gradient descent method. It takes an average of about average 15 iterations when training the Mahalanobis distance matrix. The training time for a larger dataset, like the CUHK1 dataset, takes up to one hour on a computer with a 16GB RAM, Intel i5 processor. Therefore, other variants of gradient the descent method, like stochastic gradient method and conjugate gradient method, may be tested for lower computational cost.


%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

%\section{Main Section 1}
%
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam ultricies lacinia euismod. Nam tempus risus in dolor rhoncus in interdum enim tincidunt. Donec vel nunc neque. In condimentum ullamcorper quam non consequat. Fusce sagittis tempor feugiat. Fusce magna erat, molestie eu convallis ut, tempus sed arcu. Quisque molestie, ante a tincidunt ullamcorper, sapien enim dignissim lacus, in semper nibh erat lobortis purus. Integer dapibus ligula ac risus convallis pellentesque.
%
%%-----------------------------------
%%	SUBSECTION 1
%%-----------------------------------
%\subsection{Subsection 1}
%
%Nunc posuere quam at lectus tristique eu ultrices augue venenatis. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat. Vivamus sodales tortor eget quam adipiscing in vulputate ante ullamcorper. Sed eros ante, lacinia et sollicitudin et, aliquam sit amet augue. In hac habitasse platea dictumst.
%
%%-----------------------------------
%%	SUBSECTION 2
%%-----------------------------------
%
%\subsection{Subsection 2}
%Morbi rutrum odio eget arcu adipiscing sodales. Aenean et purus a est pulvinar pellentesque. Cras in elit neque, quis varius elit. Phasellus fringilla, nibh eu tempus venenatis, dolor elit posuere quam, quis adipiscing urna leo nec orci. Sed nec nulla auctor odio aliquet consequat. Ut nec nulla in ante ullamcorper aliquam at sed dolor. Phasellus fermentum magna in augue gravida cursus. Cras sed pretium lorem. Pellentesque eget ornare odio. Proin accumsan, massa viverra cursus pharetra, ipsum nisi lobortis velit, a malesuada dolor lorem eu neque.
%
%%----------------------------------------------------------------------------------------
%%	SECTION 2
%%----------------------------------------------------------------------------------------
%
%\section{Main Section 2}
%
%Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.